PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-09 paper/app-pineappl.tex
Move appendix A.2 to the end of appendix A
Fix more Latex warnings
Fix bug in PineAPPL example

\section{Installation and usage of \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
\label{app:pineappl}

@@

@@

// we bin in rapidity from 0 to 2.4 in steps of 0.1
double bins[] = {
    0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0, 1.1, 1.2,
    1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0, 2.1, 2.2, 2.3, 2.4
};

@@

\subsection{Sample runcard for \texorpdfstring{\textsc{mg5\_aMC}}{mg5\_aMC}}
\label{app:sample-runcard}

>>>>

\section{Installation and usage of PineAPPL}
\label{app:pineappl}

@@

\subsection{Sample runcard for mg5\_aMC@NLO}
\label{app:sample-runcard}

@@

// we bin in rapidity from 0 to 2.4 in steps of 0.1
double bins[] = {
    0.0,
    0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0, 1.1, 1.2,
    1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0, 2.1, 2.2, 2.3, 2.4
};

@@
